---
title: "Participating Studies & Data Standards"
execute:
  echo: false
format: 
  html:
    page-layout: full
    toc: true
    code-fold: false
    css: styles.css
---

If you would like your study to be included in the archive, checkout our [Submission Guide](submission_guide.qmd) or contact us ([kimx3725\@umn.edu](mailto:kimx3725@umn.edu)).

::: callout-important
- An asterisk (*) in the study name indicates datasets that were not sampled or tested for disease but involved animals found dead or alive during confirmed outbreaks in the region.

- The tables below provide information only for individuals that tested positive. However, most studies also include data for individuals that tested negative for the pathogens assessed. If you would like more information about negatively tested individuals, please contact the PIs of the study of interest.
:::

## Section A: Movebank-derived Movement Data

::: callout-tip
This table is a placeholder for studies derived from Movebank. Columns match the archive data standard.
:::

```{r section A, include=FALSE}
library(DT)
library(dplyr)
library(tibble)
library(readr)
library(stringi)

data_columns <- c(
"Study Name",
"Principal Investigator",
"Animal Taxon",
"No. of Animals",
"Pathogen ID",
"Further Disease Information",
"First deployment",
"Latest deployment",
"Sensor type",
"Sample collection method",
"Sample material",
"Sample collection status",
"First sample collection date",
"Latest sample collection date",
"Detection target",
"Detection method",
"Detection outcome",
"Detection measurement",
"Detection measurement units",
"Detection measurement method details",
"Detection measurement interpretation",
"Detection limit",
"Detection limit units"
)

section_a_table <- read_csv(
  "data/master_a.csv",
  locale = locale(encoding = "Windows-1252"),
  show_col_types = FALSE
) %>%
  mutate(
    `Study Name` = sprintf(
      '<a href="%s" target="_blank">%s</a>',
      `Study URL`, `Study Name`
    ),
    
    `Principal Investigator` = mapply(function(names, emails) {

      name_vec  <- strsplit(names, ";")[[1]] |> trimws()
      email_vec <- strsplit(emails, ";")[[1]] |> trimws()

      if (length(name_vec) != length(email_vec)) {
        return(names)
      }

      links <- sprintf(
        '<a href="mailto:%s">%s</a>',
        email_vec, name_vec
      )

      paste(links, collapse = "<br>")

    }, `Principal Investigator`, `PI Email`, SIMPLIFY = TRUE),

    `Animal Taxon` = sapply(`Animal Taxon`, function(taxa) {

      if (is.na(taxa) || taxa == "") return(taxa)

      taxa_vec <- strsplit(taxa, ";")[[1]] |> trimws()

      paste(taxa_vec, collapse = "<br>")

    }),

    `Further Disease Information` = ifelse(
      !is.na(`Disease URL`) & `Disease URL` != "",
      sprintf(
        '<a href="%s" target="_blank">%s</a>',
        `Disease URL`, `Further Disease Information`
      ),
      `Further Disease Information`
    )
  ) %>%
  select(
    `Study Name`,
    `Principal Investigator`,
    `Animal Taxon`,
    `No. of Animals`,
    `Pathogen ID`,
    `Further Disease Information`,
    `First deployment`,
    `Latest deployment`,
    `Sensor type`,
    `Sample collection method`,
    `Sample material`,
    `Sample collection status`, 
    `First sample collection date`,
    `Latest sample collection date`,
    `Detection target`,
    `Detection method`,
    `Detection outcome`,
    `Detection measurement`,
    `Detection measurement units`,
    `Detection measurement method details`,
    `Detection measurement interpretation`,
    `Detection limit`,
    `Detection limit units`
  )
```

```{r section-output-A, echo=FALSE, message=FALSE, warning=FALSE}
DT::datatable(
  section_a_table,
  escape = FALSE,
  options = list(
    pageLength = 10,
    scrollX = TRUE,
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-head-nowrap', targets = "_all"),
      list(className = 'dt-nowrap', targets = "_all")   # Force no wrapping on all cells
    )
  ),
  caption = htmltools::tags$caption(
    style = "caption-side: bottom; text-align: left;",
    "Section A: Movebank-derived studies."
  )
)
```

## Section B: Private Data (Contact Required) \& External Repository Data

::: callout-tip
This table serves as a placeholder for studies that fall into one of the following categories:

- **Private datasets**: Studies that cannot be stored on Movebank due to legal, ethical, or institutional constraints, but still provide descriptive information about their datasets and contact details.

- **External repository datasets**: Studies that are already shared in other public repositories outside of Movebank.
:::

```{r Section B, include=FALSE}
# Create empty table for Section B with same columns
section_b_table <- read_csv(
  "data/master_b.csv",
  locale = locale(encoding = "Windows-1252"),
  show_col_types = FALSE
) %>%
  mutate(
    `Study Name` = sprintf(
      '<a href="%s" target="_blank">%s</a>',
      `Study URL`, `Study Name`
    ),
    
    `Principal Investigator` = mapply(function(names, emails) {

      name_vec  <- strsplit(names, ";")[[1]] |> trimws()
      email_vec <- strsplit(emails, ";")[[1]] |> trimws()

      if (length(name_vec) != length(email_vec)) {
        return(names)
      }

      links <- sprintf(
        '<a href="mailto:%s">%s</a>',
        email_vec, name_vec
      )

      paste(links, collapse = "<br>")

    }, `Principal Investigator`, `PI Email`, SIMPLIFY = TRUE),

    `Animal Taxon` = sapply(`Animal Taxon`, function(taxa) {

      if (is.na(taxa) || taxa == "") return(taxa)

      taxa_vec <- strsplit(taxa, ";")[[1]] |> trimws()

      paste(taxa_vec, collapse = "<br>")

    }),

    `Further Disease Information` = ifelse(
      !is.na(`Disease URL`) & `Disease URL` != "",
      sprintf(
        '<a href="%s" target="_blank">%s</a>',
        `Disease URL`, `Further Disease Information`
      ),
      `Further Disease Information`
    )
  ) %>%
  select(
    `Study Name`,
    `Principal Investigator`,
    `Animal Taxon`,
    `No. of Animals`,
    `Pathogen ID`,
    `Further Disease Information`,
    `First deployment`,
    `Latest deployment`,
    `Sensor type`,
    `Sample collection method`,
    `Sample material`,
    `Sample collection status`, 
    `First sample collection date`,
    `Latest sample collection date`,
    `Detection target`,
    `Detection method`,
    `Detection outcome`,
    `Detection measurement`,
    `Detection measurement units`,
    `Detection measurement method details`,
    `Detection measurement interpretation`,
    `Detection limit`,
    `Detection limit units`
  )
```

```{r section B output, output=TRUE, warning=FALSE}
DT::datatable(
  section_b_table,
  escape = FALSE,
  options = list(
    pageLength = 10,
    scrollX = TRUE,
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-head-nowrap', targets = "_all"),
      list(className = 'dt-nowrap', targets = "_all")   # Force no wrapping on all cells
    )
  ),
  caption = htmltools::tags$caption(
    style = "caption-side: bottom; text-align: left;",
    "Section B: Private Data and External Repository Data."
  )
)
```