---
title: "Participating Studies & Data Standards"
execute:
  echo: false
format: 
  html:
    page-layout: full
    toc: true
    code-fold: false
---

This initiative began in the winter of 2025. If you would like your study to be included in the archive, checkout our [Submission Guide](submission_guide.qmd) or contact us ([kimx3725\@umn.edu](mailto:kimx3725@umn.edu)). 

## Section A: Movebank-derived Movement Data

::: callout-tip
This table is a placeholder for studies derived from Movebank. Columns match the archive data standard.
:::

```{r section A, include=FALSE}
library(DT)
library(dplyr)

# Define the data standard variables
data_columns <- c(
  "Study Name",
  "Principal Investigator",
  "Animal Taxon",
  "No. of Animals",
  "First deployment",
  "Latest deployment",
  "Sensor type",
  "Pathogen ID",
  "Sample collection method",
  "Sample material",
  "First sample collection date",
  "Latest sample collection date",
  "Detection target",
  "Detection method",
  "Detection outcome",
  "Detection measurement",
  "Detection measurement units",
  "Detection measurement method details",
  "Detection measurement interpretation",
  "Detection limit",
  "Detection limit units"
)

# Create empty placeholder table for Section A
section_a_table <- tibble::tibble(
  !!!setNames(rep(list(character()), length(data_columns)), data_columns)
)

# Add a study row (replace what you know, leave NA where unknown) ---- 
new_study <- tibble(
  "Study Name" = '<a href="https://doi.org/10.5441/001/1.323" target="_blank">
                    Bobcat; Central California, USA
                  </a>',
  "Principal Investigator" = '<a href="mailto:lekserieys@gmail.com"> 
                    Laurel Serieys
                    </a>',
  "Animal Taxon" = "Lynx rufus",
  "No. of Animals" = "3",
  "First deployment" = "2017/07/14",
  "Latest deployment" = "2018/12/28",
  "Sensor type" = "GPS",
  "Pathogen ID" = "Notoedric mange (Notoedres cati)",
  "Sample collection method" = NA,
  "Sample material" = NA,
  "First sample collection date" = "2018/02/25",
  "Latest sample collection date" = "2018/12/28",
  "Detection target" = NA,
  "Detection method" = "Visual",
  "Detection outcome" = "Dead/Rehabilitated",
  "Detection measurement" = NA,
  "Detection measurement units" = NA,
  "Detection measurement method details" = NA,
  "Detection measurement interpretation" = NA,
  "Detection limit" = NA,
  "Detection limit units" = NA
)

section_a_table <- bind_rows(section_a_table, new_study)
```

# Output chunk
```{r section-output-A, echo=FALSE, message=FALSE, warning=FALSE}
DT::datatable(
  section_a_table,
  options = list(
    pageLength = 10,
    scrollX = TRUE,
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-head-nowrap', targets = "_all")
    )
  ),
  escape = FALSE,
  caption = htmltools::tags$caption(
    style = "caption-side: bottom; text-align: left;",
    "Section A: Movebank-derived studies"
  )
)
```

## Section B: Private Data (Contact Required) \& External Repository Data

::: callout-tip
This table serves as a placeholder for studies that fall into one of the following categories:

- **Private datasets**: Studies that cannot be stored on Movebank due to legal, ethical, or institutional constraints, but still provide descriptive information about their datasets and contact details.

- **External repository datasets**: Studies that are already shared in other public repositories outside of Movebank.
:::

```{r Section B, include=FALSE}
# Create empty table for Section B with same columns

section_b_table <- tibble::tibble(
!!!setNames(rep(list(character()), length(data_columns)), data_columns)
)
```

```{r section B output, output=TRUE, warning=FALSE}
DT::datatable(
section_b_table,
options = list(
pageLength = 10,
scrollX = TRUE,
autoWidth = TRUE
),
caption = htmltools::tags$caption(
style = "caption-side: bottom; text-align: left;",
"Section B: Private Data and External Repository Data. (empty template)."
)
)
```